%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Thomas }{Noelcke}
\mobile{(971) 645 - 1311} 
%%% Social
\email{noelcket@gmail.com}
\github{tnoelcke}
\linkedin{https://www.linkedin.com/in/thomas-noelcke-9b22aa14a/}
%%% Optionals
\position{Systems Development Engineer}
\quote{``Anything worth engineering is worth over-engineering."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Hiring Team}
  {
  Digital Ocean\newline \hfill
  }
\letterdate{\today}
\lettertitle{Job Application for Software Engineer: Database-as-a-Service}
\letteropening{\newline \hfill Dear Hiring Team,}
\letterclosing{Sincerely,}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Thomas Noelcke~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Game Plan:
%%% Intro
%%% Automation
%%% Address lack of experience with GO. - Quick learner
%%% 


%%% Write content for your cover letter
\begin{cvletter}
    I recently learned that Digital Ocean is seeking a highly-motivated Software Engineer. I am excited to apply for this position because I am enthusiastic about the opportunity to contribute to the cloud. I am confident that with my previous experience and ability to pick up new technology quickly that I can hit the ground running and provide value at Digital Ocean.\\
    
    During my time at the Center for Applied Systems and Software (CASS) I advocated for writing testable and maintainable code. On my projects we used many tools to create testable and maintainable code. One tool was dependency injection. This allowed us to target our tests to specific code allowing us to quickly pinpoint problems. We also used code coverage metrics as well as static analysis to ensure code quality. I will leverage this experience at Digital Ocean to build high quality software applications.\\
    
    I may not have experience with GO but I am confident that I can hit the ground running and learn GO on the job. Through my experience at CASS I have proven that I can hit the ground running and provide value in short order. When I first started at CASS as a Systems Development Engineer I had little experience running and managing application development projects. However, I was able to hit the ground running and learn new technologies quickly. At CASS I worked in may different platforms including, Swift, JavaScript, TypeScript, Python, C\#, Java and C++. I am confident that my experience working on many different languages at multiple levels will be put to good use at Digital Ocean.\\ 
    
    Another asset that I bring to Digital Ocean is my superior communication and customer service skills. While working at CASS I managed multiple projects for multiple stakeholders at one time. At any given time I was managing 3 to 6 development projects. As a Systems Development Engineer I was responsible for communicating with the client, prioritizing the backlog and working with my team to implement client vision. My experience working directly with customers will prove to be a valuable asset to your team.\\ 
    
    I am confident that my unique qualifications and background will add value at Digital Ocean. My experience building high quality code at multiple levels, communicating with clients and learning quickly with be an asset to your organization. I look forward to meeting with you to discuss my qualifications for the Software Engineer position at Digital Ocean. Thank you for your time and consideration.\\
    

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
