%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Thomas }{Noelcke}
\mobile{(971) 645 - 1311} 
%%% Social
\email{noelcket@gmail.com}
\github{tnoelcke}
\linkedin{https://www.linkedin.com/in/thomas-noelcke-9b22aa14a/}
%%% Optionals
\position{Systems Development Engineer}
\quote{``Anything worth engineering is worth over-engineering."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Hiring Team}
  {
  esha Research\newline \hfill
  }
\letterdate{\today}
\lettertitle{Job Application for C\# Developer}
\letteropening{\newline \hfill Dear Hiring Team,}
\letterclosing{Sincerely,}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Thomas Noelcke~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Game Plan:
%%% Intro
%%% Automation
%%% Address lack of experience with GO. - Quick learner
%%% 


%%% Write content for your cover letter
\begin{cvletter}
    I recently learned that esha Research is seeking a highly motivated Software Engineer. I am excited to apply for this position because I am passionate about software development. I am confident that my previous experience at the Center for Applied Systems and Software will make me an excellent candidate for this position.\\
    
    During my time at the Center for Applied Systems and Software (CASS) I worked on many different projects in different technologies. Often I was pulled onto partially completed projects or existing code bases. It was also common for me to work on multiple projects at the same time. Through this experience I have learned to quickly navigate projects and implement new features with little guidance. I have also learned to quickly process business requirements and translate them into feature complete code.\\
    
    I am passionate about producing the highest quality software possible in a team environment. While at CASS, in addition to implementing CI and CD, I also explored other code quality measure such as static analysis, linting, unit testing and code reviews. To ensure high quality code I started by implementing a code review policy allowing members of the team to review each others code. I also integrated static analysis, linting, and code coverage metrics into our CI pipelines. Using these methods we were able to produce higher quality code with fewer bugs. I am confident that I can use this experience to help improve the code review process at esha Research.\\
    
    While at CASS I also had the opportunity to mentor and be mentored. At CASS we hired students to complete client software work. As a Software Developer at CASS I was mentored on software development projects by the senior staff. After a year of working at CASS I was promoted to a Senior Level position. While working as a Systems Development Engineer I supervised and mentored students on how to complete critical aspects of software development. I am confident that my experience working at CASS will help me quickly integrate into and contribute to your team.\\
    
    I am confident that my unique qualifications and background will add value at esha Research. I look forward to meeting with you to discuss my qualifications for the Software Engineer position at esha Research. Thank you for your time and consideration.\\
    

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
