%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Thomas }{Noelcke}
\mobile{(971) 645 - 1311} 
%%% Social
\email{noelcket@gmail.com}
\github{tnoelcke}
\linkedin{https://www.linkedin.com/in/thomas-noelcke-9b22aa14a/}
%%% Optionals
\position{Systems Development Engineer}
\quote{``Anything worth engineering is worth over-engineering."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Hiring Team}
  {
  Twitter\newline \hfill
  }
\letterdate{\today}
\lettertitle{Job Application for Software Engineer, Backend - Tweet Services}
\letteropening{\newline \hfill Dear Hiring Team,}
\letterclosing{Sincerely,}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Thomas Noelcke~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Game Plan:
%%% Intro
%%% Automation
%%% Address lack of experience with GO. - Quick learner
%%% 


%%% Write content for your cover letter
\begin{cvletter}
    I recently learned that Twitter is seeking a highly motivated Software Engineer. I am excited to apply for this position because I am enthusiastic about the opportunity to test my skills on a large platform. I am confident that my previous experience at the Center for Applied Systems and Software will make me an excellent candidate for this position.\\
    
    During my time at the Center for Applied Systems and Software (CASS) I advocated for and implemented continuous integration and continuous deployment. Previously, most deployments were done manually and quality control measures were not run prior to deployment. When I first started I was quick to find a better way to handle deployments. By automating deployments I was able to improve the quality, reliability and speed of delivery at CASS. I plan to put my desire to automate and improve the software development process to work at Twitter.\\
    
    I am also passionate about producing the highest quality software possible in a team environment. While at CASS, in addition to implementing CI and CD, I also explored other code quality measure such as static analysis, linting, unit testing and code reviews. To ensure high quality code I started by implementing a code review policy allowing members of the team to review each others code. I also integrated static analysis, linting, and code coverage metrics into our CI pipelines. Using these methods we were able to produce higher quality code with fewer bugs.\\
    
    While at CASS I also had the opportunity to mentor and be mentored. At CASS we hired students to complete client software work. As a Software Developer at CASS I was mentored on software development projects by the senior staff. After a year of working at CASS I was promoted to a Senior Level position. While working as a Systems Development Engineer I supervised and mentored students on how to complete critical aspects of software development. When trying to solve difficult problems I would often pair program with students helping them understand and approach the problem at hand. I am confident that my experience working at CASS will help me quickly integrate into and contribute to your team.\\
    
    I am confident that my unique qualifications and background will add value at Twitter. I look forward to meeting with you to discuss my qualifications for the Software Engineer position at Digital Ocean. Thank you for your time and consideration.\\
    

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
